Millions of Type Errors

### 2023-04-18 oopsla23/paper.tex
type errors overview, 1st draft

@@

\begin{figure}[t]
\begin{tabular}{rl}
 5,001 & total logs \\
       & 4,471 nocheck + 506 nonstrict + 24 strict \\
 182,247 & total forced strict type errors \\
       & {83,005 in module, 5,113 in edit regions} \\
  1,521 & total type errors \\
       & {1,035 in module, 110 non-syntax + 47 syntax in edit regions}
  \\[2ex]

@@

  \begin{minipage}{0.5\textwidth}
    \begin{tabular}{rr}
      Session length & \# Sessions \\\midrule
      1 &  450 \\
      2 &  199 \\
      3 &  129 \\
      4 &  73 \\
      5 &  60 \\
      6-10 & 150 \\
      11-20 & 67 \\
      21-40 & 11 \\
      >40 & 7
      %% max 393
    \end{tabular}
  \end{minipage}\begin{minipage}{0.5\textwidth}
    \begin{tabular}{rr}
      Time delta & \# Records \\\midrule
      <=0ms & 0 \\
      0-5ms & 284 \\
      5-1000ms & 248 \\
      1-2s & 153 \\
      2-5s & 232 \\
      5-10s & 207 \\
      10-30s & 524 \\
      30-60s & 392 \\
      1-2m & 394 \\
      2-5m & 559 \\
      5-10m & 360 \\
      >10-60m & 502
    \end{tabular}
  \end{minipage}

@@

>>>>

Analysis pipeline to be freely available.
Data may be available, depends on Roblox.

@@

\begin{figure}[t]
  %% TODO split counts, total = current + previous
  \begin{tabular}{rl}
   5,001 & total logs \\
         & 4,471 nocheck + 506 nonstrict + 24 strict \\
   182,247 & total forced strict type errors \\
         & {83,005 in module, 5,113 in edit regions} \\
    1,521 & total type errors \\
         & {1,035 in module, 110 non-syntax + 47 syntax in edit regions}
    \\[2ex]

@@

  %% TODO these need to be plots, it's too much reading for the quick takeaway
  %% put exactly this data into bars!
  \begin{minipage}[t]{0.5\textwidth}
    \begin{tabular}{rr}
      Session length & \# Sessions \\\midrule
      1 &  450 \\
      2 &  199 \\
      3 &  129 \\
      4 &  73 \\
      5 &  60 \\
      6-10 & 150 \\
      11-20 & 67 \\
      21-40 & 11 \\
      >40 & 7
      %% max 393
    \end{tabular}
  \end{minipage}\begin{minipage}[t]{0.5\textwidth}
    \begin{tabular}{rr}
      Time delta & \# Records \\\midrule
      0-5ms & 284 \\
      5-1000ms & 248 \\
      1-2s & 153 \\
      2-5s & 232 \\
      5-10s & 207 \\
      10-30s & 524 \\
      30-60s & 392 \\
      1-2m & 394 \\
      2-5m & 559 \\
      5-10m & 360 \\
      >10-60m & 502
    \end{tabular}
  \end{minipage}

@@

\begin{figure}[t]
  %% TODO draw bars or curves b/c numbers are too hard to compare horizontally

  TODOD table: mode (fs), project, module, region; cell olde,curr; two rows per actual mode ... or two tables

  Errors in edit region.
  Each record with an edit region error adds +1 to at least 1 row.

  \begin{tabular}{lrrr}
    Error Label & \# Added & \# Persist & \# Remove \\\midrule
    CodeTooComplex
    & 0 & 0 & 0 \\
    UnificationTooComplex
    & 0 & 0 & 0 \\[1ex]
    SyntaxError
    & 30 & 0 & 76 \\
    UnknownSymbol
    & 12 & 14 & 19 \\
    UnknownProperty
    & 3 & 1 & 4 \\
    UnknownRequire
    & 1 & 5 & 0 \\
    GenericError
    & 1 & 0 & 1 \\
    CountMismatch
    &  1 &  0 &  1 \\
    OptionalValueAccess
    &  0 &  0 &  1 \\
  \end{tabular}

  \caption{Errors overview}
  \label{f:errors-overview}
\end{figure}
